5'CutSiteAnalysisDataGeneration

### 2022-12-02 R/5'CutSiteAnalysisDataGeneration.rmd
Added code for sequence logo input generation
-Note to self: Don't generate data for a paper again without documenting how it was generated :(
- I should probably rename/rework this script since it doesn't (and probably shouldn't) deal exclusively with the 5' end of sequences.

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                           queryPattern, sequencesName, readMinMax,
                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE) {
  readData = fread(generateFilePath(
    directory, dataTypeStrings$alignedReads , ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= readMinMax[1] & Read_Length <= readMinMax[2]]

@@

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE)
```

>>>>

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                           queryPattern, sequencesName, readMinMax,
                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE,
                           alsoCreateSequenceLogoInput = FALSE) {
  readData = fread(generateFilePath(
    directory, dataTypeStrings$alignedReads , ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= readMinMax[1] & Read_Length <= readMinMax[2]]

@@

  if (alsoCreateSequenceLogoInput) {
    write(str_sub(readData$Read_Sequence, 1, 17), sep = '\n', file = generateFilePath(
      directory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = FIVE_PRIME, filtering = filtering
    ))
    write(str_sub(readData$Read_Sequence, -14, -1), sep = '\n', file = generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = THREE_PRIME, filtering = filtering
    ))
  }

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
```
